---
title: "Ameke"
author: "DavidSon"
date: "2024-01-28"
output: html_document
---

```{r plot_code, echo=FALSE}
library(readxl)
library(dplyr)
library(tidyverse)
library(tidyr)
library(readr)
library(openxlsx)
library(ggplot2)
library(rmarkdown)
library(rlang)
```


#Import data

```{r}
AM<- read_xlsx("Result/Mastercombinereasultlist.xlsx", sheet = "SheetB")
```

```{r}
AM2<- select(AM, Nox2018, Nox2019, Nox2020,Windspeed_Averageweekly2018, Temperature_Averageweekly2018, Windspeed_Averageweekly2019, Temperature_Averageweekly2019,Windspeed_Averageweekly2020, Temperature_Averageweekly2020, Noxemission_2018, Noxemission_2019, Noxemission_2020)
```




#Graph1<-
```{r}
df_long <- AM2 %>%
  pivot_longer(cols = everything(),
               names_to = c(".value", "Year"),
               names_pattern = "(\\D+)(\\d+)")
```

```{r}
# List of dependent variable names
dependent_vars <- c("Windspeed_Averageweekly", "Temperature_Averageweekly", "Nox")
```

#NOXEmission

#GraphA<-
```{r}
# Plot graph with trendlines
GraphA<-ggplot(df_long, aes(x = Noxemission_ , y =Temperature_Averageweekly, color = Year)) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dotted") +
  geom_point() +
  facet_wrap(~ 'AverageWeekly_Trendlines of NoxEmission & Temp (2018_2020)', scales = "free_y") +
  labs(x = "Noxemission", y = "Temperature_Averageweekly", color = "Years") +
  theme_minimal()+
  
  geom_text(data = equations_df, aes(label =paste(X.Year.2018...y...1.45.x..47.42.R.2...0.81.,X.Year.2019...y...1.49.x..50.56.R.2...0.83.,X.Year.2020...y...0.93.x..28.15.R.2...0.55.),x = Inf, y = -Inf, hjust = 1, vjust = 0), size = 2.5)
```



#GraphB<-
```{r}
# Plot graph with trendlines
GraphB<-ggplot(df_long, aes(x = Noxemission_ , y =Windspeed_Averageweekly, color = Year)) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dotted") +
  geom_point() +
  facet_wrap(~ 'AverageWeekly_Trendlines of NoxEmission & Windspeed (2018_2020)', scales = "free_y") +
  labs(x = "Noxemission", y = "Windspeed_Averageweekly", color = "Years") +
  theme_minimal()+
  geom_text(data = equations_df2, aes(label =paste(X.Year.2018...y....0.02.x..2.83.R.2...0.09.,X.Year.2019...y....0.05.x..4.31.R.2...0.36.,X.Year.2020...y....0.05.x..4.38.R.2...0.3.),x = Inf, y = -Inf, hjust = 1, vjust = 0), size = 2.5)
```
#GraphC<-
```{r}
# Plot graph with trendlines
GraphC<-ggplot(df_long, aes(x = Noxemission_ , y =Nox, color = Year)) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dotted") +
  geom_point() +
  facet_wrap(~ 'AverageWeekly_Trendlines of NoxEmission & Windspeed (2018_2020)', scales = "free_y") +
  labs(x = "Noxemission", y = "Noxconcentration", color = "Years") +
  theme_minimal()+
  geom_text(data = equations_df3, aes(label =paste(X.Year.2018...y....0.06.x..3.41.R.2...0.43.,X.Year.2019...y....0.05.x..2.72.R.2...0.4.,X.Year.2020...y....0.02.x..1.26.R.2...0.46.),x = Inf, y = -Inf, hjust = 1, vjust = 0), size = 2.5)
```









#Noxconentration

#Graph4<-
```{r}
# Plot graph with trendlines
Graph4<-ggplot(df_long, aes(x = Temperature_Averageweekly, y =Nox , color = Year)) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dotted") +
  geom_point() +
  facet_wrap(~ 'AverageWeekly_Trendlines of Noxconcentration & Temp (2018_2020)', scales = "free_y") +
  labs(x = "Temperature_Averageweekly", y = "Noxconcentration", color = "Years") +
  theme_minimal()+
  geom_text(data = equations_df4, aes(label =paste(X.Year.2018...y....13.41.x..20.97.R.2...0.65.,X.Year.2019...y....15.31.x..20.46.R.2...0.5.,X.Year.2020...y....32.44.x..23.44.R.2...0.59.),x = Inf, y = -Inf, hjust = 1, vjust = 0), size = 2.5)
```

#Graph5<-
```{r}
# Plot graph with trendlines
Graph5<-ggplot(df_long, aes(x =Windspeed_Averageweekly, y =Nox , color = Year)) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dotted") +
  geom_point() +

  facet_wrap(~ 'AverageWeekly_Trendlines of Noxconcentration & Windspeed (2018_2020)', scales = "free_y") +
  labs(x = "Windspeed_Averageweekly", y = "Noxconcentration", color = "Years") +
  theme_minimal()+
  geom_text(data = equations_df5, aes(label =paste(X.Year.2018...y....0.07.x..2.19.R.2...0.01.,X.Year.2019...y...0.28.x..1.98.R.2...0.06.,X.Year.2020...y...1.72.x..1.51.R.2...0.28.),x = Inf, y = -Inf, hjust = 1, vjust = 0), size = 2.5)

```

#MultipleregressionZone

```{r}
# Convert "Year" to a factor with specified levels
df_long$Year <- factor(df_long$Year, levels = c("2018", "2019", "2020"))
```

```{r}
# Perform multiple linear regressions for each dependent variable
models <- lapply(dependent_vars, function(dependent_var) {
  lm(as.formula(paste(dependent_var, "~Noxemission_ + Year")), data = df_long)
})

```

```{r}
# Summaries of the regression models
 lapply(models, summary)
```

```{r}
#Combine the models with their respective dependent variable names
named_models <- setNames(models, dependent_vars)

# Print the named models
print(named_models)
```
```{r}
# Create a linear regression model
model2 <- lm(Noxemission_ ~ Year + Nox + Windspeed_Averageweekly + Temperature_Averageweekly, data = df_long)


```
summary(model2)









```{r}
# Export plot to PDF
#ggsave("plotNoxcentrationwind.pdf", plot = , width = 8, height = 6)
# Export plot to PDF
#ggsave("plot.pdf", plot, width = 8, height = 6)
```


#Export Graphs

```{r}
 #List of plot objects
plot_list <- list(plot1 = GraphA, plot2 = GraphB, plot3 = GraphC, plot4=Graph4, plot5=Graph5)

# Export all plots to PDF
invisible(lapply(names(plot_list), function(x) ggsave(paste0(x, ".pdf"), plot = plot_list[[x]], width = 8, height = 6)))

```





#Equation of line region
#Grph1text
```{r}
# Calculate and annotate equation of the line and R-squared value for each year
equations <- lapply(unique(df_long$Year), function(year) {
  sub_df <- subset(df_long, Year == year)
  model <- lm(Temperature_Averageweekly ~ Noxemission_, data = sub_df)
  eq <- paste("Year", year, ": y =", round(coef(model)[2], 2), "x", round(coef(model)[1], 2), "R^2 =", round(summary(model)$r.squared, 2))
  return(eq)
})
# Create a dataframe with Year and Equation columns
equations_df <- data.frame(Year = unique(df_long$Year), equations)
#colnames(equations_df)
```

#Grph2text
```{r}
# Calculate and annotate equation of the line and R-squared value for each year
equations2 <- lapply(unique(df_long$Year), function(year) {
  sub_df <- subset(df_long, Year == year)
  model <- lm(Windspeed_Averageweekly ~ Noxemission_, data = sub_df)
  eq <- paste("Year", year, ": y =", round(coef(model)[2], 2), "x+", round(coef(model)[1], 2), "R^2 =", round(summary(model)$r.squared, 2))
  return(eq)
})
# Create a dataframe with Year and Equation columns
equations_df2 <- data.frame(Year = unique(df_long$Year), equations2)
#colnames(equations_df2)

```

#Graph3
```{r}
# Calculate and annotate equation of the line and R-squared value for each year
equations3 <- lapply(unique(df_long$Year), function(year) {
  sub_df <- subset(df_long, Year == year)
  model <- lm(Nox ~ Noxemission_, data = sub_df)
  eq <- paste("Year", year, ": y =", round(coef(model)[2], 2), "x+", round(coef(model)[1], 2), "R^2 =", round(summary(model)$r.squared, 2))
  return(eq)
})
# Create a dataframe with Year and Equation columns
equations_df3 <- data.frame(Year = unique(df_long$Year), equations3)
#colnames(equations_df3)

```


#Graph4
```{r}
# Calculate and annotate equation of the line and R-squared value for each year
equations4 <- lapply(unique(df_long$Year), function(year) {
  sub_df <- subset(df_long, Year == year)
  model <- lm(Temperature_Averageweekly ~ Nox, data = sub_df)
  eq <- paste("Year", year, ": y =", round(coef(model)[2], 2), "x+", round(coef(model)[1], 2), "R^2 =", round(summary(model)$r.squared, 2))
  return(eq)
})
# Create a dataframe with Year and Equation columns
equations_df4 <- data.frame(Year = unique(df_long$Year), equations4)
#colnames(equations_df4)

```

#Graph5
```{r}
# Calculate and annotate equation of the line and R-squared value for each year
equations5 <- lapply(unique(df_long$Year), function(year) {
  sub_df <- subset(df_long, Year == year)
  model <- lm(Windspeed_Averageweekly ~ Nox, data = sub_df)
  eq <- paste("Year", year, ": y =", round(coef(model)[2], 2), "x+", round(coef(model)[1], 2), "R^2 =", round(summary(model)$r.squared, 2))
  return(eq)
})
# Create a dataframe with Year and Equation columns
equations_df5 <- data.frame(Year = unique(df_long$Year), equations5)
#colnames(equations_df5)

```



```





